---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw3biostat625

<!-- badges: start -->
[![R-CMD-check](https://github.com/jianxion/hw3biostat625/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jianxion/hw3biostat625/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jianxion/hw3biostat625/branch/master/graph/badge.svg)](https://app.codecov.io/gh/jianxion/hw3biostat625?branch=master)
<!-- badges: end -->

## Overview
Since this is just a practice for creating a r package, this package only
contains one function called `my.lm()`. This function helps you to fit a simple
or multiple linear regression on a dataset. The output will contain a table of
coefficients, calculated R-squared and ajusted R-squared value, F statistic with
degree of freedoms. These outputs are the same as R built-in summary.lm() function
gives you, but the `my.lm()` function's output will also contain three 
plots to help you check the assumptions of "LINE"" of a linear regression model.

## Installation

You can install the development version of hw3biostat625 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jianxion/hw3biostat625")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hw3biostat625)
## basic example code
```

Here is an example of fitting a multiple linear regression model on the
mtcars dataset. The target variable is mpg and the predictors are disp, hp,
and drat. 

```{r cars}
x = mtcars[, c(3,4,5)]
y = mtcars$mpg
mymodel <- my.lm(x, y)
```



