---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
if (!require("bench")) install.packages("bench")
library(bench)
```

Since this is just a practice for creating a r package, this package only
contains one function called my.lm(). This function basically does the same job
as R built-in summary.lm() function, but the output will also contain three 
plots to help you check the assumptions of a linear regression model.

After installing this r package, type this command to utilize functions inside the package.

```{r setup}
library(hw3biostat625)
```

## Data: mtcars
To explore the usage of the my.lm() function, we'll use the R built-in dataset mtcars
as an example. Here is a brief overview of this dataset.

```{r}
head(mtcars)
dim(mtcars)
summary(mtcars)
```

## Use the `my.lm()` function
```{r}
x = mtcars[, c(3,4,5)]

y = mtcars$mpg

mymodel <- my.lm(x, y)
```



## Compare with R built-in `lm()` function
```{r, message = FALSE}
model = lm(mpg ~ disp + hp + drat, data = mtcars)

summary(model)$coef

all.equal(mymodel[,1] , summary(model)$coef[,1])

all.equal(mymodel[,2] , summary(model)$coef[,2])

all.equal(mymodel[,3] , summary(model)$coef[,3])

all.equal(mymodel[,4] , summary(model)$coef[,4])

all.equal(mymodel , summary(model)$coef)
```



```{r, message = FALSE}
result = bench::mark(mymodel, summary(model)$coef)
print(result)
```










